### 2023-06-01 paper/localpsf.tex
edited writing in stokes section

The pressure, $\pressure$, is discretized with first order scalar continuous Galerkin finite elements defined on a mesh of tetrahedra. The velocity, $\velocity$, is discretized with second order continuous Galerkin finite elements on the same mesh. The parameter $\basalfriction$ is discretized with first order scalar continuous Galerkin finite elements on the mesh of triangles that results from restricting the tetrahedral mesh to the basal boundary, $\Gamma_b$. Note that $\Gamma_b$ is a 2D surface embedded in 3D due to the mountain topography. We also generate a flattened version of $\Gamma_b$, denoted by $\Omega \subset \mathbb{R}^2$, by ignoring the height coordinate. The parameter $\basalfriction$ is dually viewed as a function on $\Gamma_b$ for the purpose of solving the Stokes equations, and as a function on $\Omega$ for the purpose of building our Hessian approximations and defining the regularization. 
%This flattening is necessary because our operator approximation method requires adding points on this surface together to get other points on the surface, and this is only well-defined in flat space. 
The observations are generated by adding multiplicative
Gaussian noise to the tangential component of the velocity field
restricted to the top surface of the geometry. We use $5\%$ noise in all cases, except for Figure \ref{fig:stokes_reconstructions} and Table \ref{fig:condition_number} where the noise is varied from $1\%$ to $25\%$. The true basal sliding
coefficient field and the true velocity field, which is obtained by
solving~\eqref{Stokeseqn}, are shown in Figure~\ref{fig:true_beta_u}.

@@

In Table~\ref{tab:condition_number}, we show the condition number of the preconditioned Hessian using our preconditioners, for a variety of noise levels ranging from $1\%$ to $25\%$. The condition number using our PSF preconditioners is extremely small (ranging between 1 and 10) and relatively stable over this range of noise levels. PSF (25) performs slightly better than PSF(5), which performs better than PSF (1), as expected. All PSF preconditioners outperform no preconditioning and regularization preconditioning for all noise levels. No preconditioning outperforms regularization preconditioning for all noise levels except $25\%$. We report condition number results for the preconditioned Hessian, $\mathbf{H}$, demonstrating that the PSF preconditioners built based on the Gauss-Newton Hessian, $\bm{H}_\text{gn}$, are also good preconditioner for $\bm{H}$.
%As expected, regularization preconditioning performs well for large $\gamma$ and poorly for small $\gamma$. Our PSF preconditioners outperform no preconditioning and regularization preconditioning for medium and small $\gamma$, and perform similarly to regularization preconditioning for large~$\gamma$.

>>>>

The pressure, $\pressure$, is discretized with first order scalar continuous Galerkin finite elements defined on a mesh of tetrahedra. The velocity, $\velocity$, is discretized with second order continuous Galerkin finite elements on the same mesh. The parameter $\basalfriction$ is discretized with first order scalar continuous Galerkin finite elements on the mesh of triangles that results from restricting the tetrahedral mesh to the basal boundary, $\Gamma_b$. Note that $\Gamma_b$ is a 2D surface embedded in 3D due to the mountain topography. We also generate a flattened version of $\Gamma_b$, denoted by $\Omega \subset \mathbb{R}^2$, by ignoring the height coordinate. The parameter $\basalfriction$ is dually viewed as a function on $\Gamma_b$ for the purpose of solving the Stokes equations, and as a function on $\Omega$ for the purpose of building our Hessian approximations and defining the regularization. 
%This flattening is necessary because our operator approximation method requires adding points on this surface together to get other points on the surface, and this is only well-defined in flat space. 
The observations are generated by adding multiplicative
Gaussian noise to the tangential component of the velocity field
restricted to the top surface of the geometry. We use $5\%$ noise in all cases, except for Figure \ref{fig:stokes_reconstructions} and Table \ref{tab:condition_number} where the noise is varied from $1\%$ to $25\%$. The true basal sliding
coefficient field and the true velocity field, which is obtained by
solving~\eqref{Stokeseqn}, are shown in Figure~\ref{fig:true_beta_u}.

@@

In Table~\ref{tab:condition_number}, we show the condition number of the preconditioned Hessian using our preconditioners, for a variety of noise levels ranging from $1\%$ to $25\%$. The condition number using our PSF preconditioners is extremely small (ranging between 1 and 10) and relatively stable over this range of noise levels. PSF (25) performs better than PSF(5), which performs better than PSF (1), as expected. All PSF preconditioners outperform no preconditioning and regularization preconditioning for all noise levels. No preconditioning outperforms regularization preconditioning for all noise levels except $25\%$. We report condition number results for the preconditioned Hessian, $\mathbf{H}$, demonstrating that the PSF preconditioners built based on the Gauss-Newton Hessian, $\bm{H}_\text{gn}$, are also good preconditioner for $\bm{H}$.
%As expected, regularization preconditioning performs well for large $\gamma$ and poorly for small $\gamma$. Our PSF preconditioners outperform no preconditioning and regularization preconditioning for medium and small $\gamma$, and perform similarly to regularization preconditioning for large~$\gamma$.
